---
title: "Distributions of epidemiological quantities"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
---

loading useful packages 

```{r,eval=FALSE}
library("ggplot2")
library(scales) # for function alpha()
library("moments", lib.loc="~/Library/R/3.2/library")
library("cowplot", lib.loc="~/Library/R/3.2/library")
library("gridExtra", lib.loc="~/Library/R/3.2/library")
library("grid", lib.loc="/Library/Frameworks/R.framework/Versions/3.2/Resources/library")
library("plyr", lib.loc="~/Library/R/3.2/library")
```

# Loading  simulation outputs

(given that we don't need information on the distribution for each single simulation, 
we _only take the mean, overall all runs per each index-case_)

## custom function to load epi. quant. from 'combined' and 'pure-aerosol' models

```{r}

epi_loading_fun <- function(my_path) {
  
  # create empty data-frame
  epi_quantities_df <- data.frame()

    # list simulations, for all idx-case
    files <- sort(list.files(path= my_path , pattern="*.csv", full.names=T))
    
    for(f_name in files) {
        
        new_df<- read.csv(f_name, header=FALSE)
        idx<- new_df[1,1]

        # only save mean  for each epidemiological quantity
        epi_quantities_df <- rbind(epi_quantities_df,
                             data.frame(idx,
                                        mean(new_df[,4]),
                                        mean(new_df[,5]),
                                        mean(new_df[,6])
                             )
        )

    }

# assign columns names
colnames(epi_quantities_df) <- c('idxc','mean_i_tot','mean_time_to_peak','mean_max_time ')

# sorting case according to idx-case
epi_quantities_df <- arrange(epi_quantities_df,epi_quantities_df$idxc)

epi_quantities_df
}
```

## custom function to load epi. quant. from 'pure-droplet' model

```{r}

droplet_loading_fun <- function(my_path) {
  
  # create empty data-frame
  epi_quantities_df <- data.frame()

    # list simulations, for all idx-case
    files <- sort(list.files(path= my_path , pattern="*.csv", full.names=T))
    
    for(f_name in files) {
        
        new_df<- read.csv(f_name, header=FALSE)
        idx<- new_df[1,1]

        # only save mean  for each epidemiological quantity
        epi_quantities_df <- rbind(epi_quantities_df,
                             data.frame(idx,
                                        mean(new_df[,2]),
                                        mean(new_df[,3]),
                                        mean(new_df[,4])
                             )
        )

    }

# assign columns names
colnames(epi_quantities_df) <- c('idxc','mean_i_tot','mean_time_to_peak','mean_max_time ')

# sorting case according to idx-case
epi_quantities_df <- arrange(epi_quantities_df,epi_quantities_df$idxc)

epi_quantities_df
}
```

## function to load  $R_{0}$

```{r,eval=FALSE}

r0_load_funcion <- function(my_path){

  help_df <- data.frame() # define help data-frame
  
    # list idx-case simulations for each ACR condition
    files <- sort(list.files(path = my_path , pattern="*.csv", full.names=T))

        for(f_name in files) {
        
            new_df<- read.csv(f_name, header=FALSE)
            idx<- new_df[1,1]
             
            # compute mean
            help_df <- rbind(help_df,data.frame(idx, mean(new_df[,2]) )) 
    }

    
# assign right names to columns
colnames(help_df) <- c('idxc','mean_r0')

# sorting case according to idx-case
help_df <- arrange(help_df,help_df$idxc)

help_df
}
```

## call function for  $R_{0}$

```{r,eval=FALSE}
r0_aero_df <- r0_load_funcion("~/Documents/school_net_proj/r0/aero_model_r0/ACR05")
r0_comb_df <- r0_load_funcion("~/Documents/school_net_proj/r0/comb_model_r0/ACR05")
r0_drop_df <- r0_load_funcion("~/Documents/school_net_proj/r0/drop_model_r0/ACR05")

```


## call epi. quant. loading function

```{r,eval=FALSE}

# loop over subdirectories ~ ACR conditions  ...
aero_epi_df <- epi_loading_fun("~/Documents/school_net_proj/aerolsol_model_outputs/ACR05") 
# add R0
aero_epi_df['mean_r0'] <- r0_aero_df$mean_r0
# add column with model name
aero_epi_df['model'] <- rep('aerosol',nrow(aero_epi_df))

comb_epi_df <- epi_loading_fun("~/Documents/school_net_proj/comb_alpha_05_out/ACR05")
# add R0 
comb_epi_df['mean_r0'] <- r0_comb_df$mean_r0
# add column with model name
comb_epi_df['model'] <- rep('combined',nrow(aero_epi_df))

drop_epi_df <- droplet_loading_fun('~/Documents/school_net_proj/droplet_model_out')
# add R0
drop_epi_df['mean_r0'] <- r0_drop_df$mean_r0
# add column with model name
drop_epi_df['model'] <- rep('droplet',nrow(aero_epi_df))
```

## merge 3 data frames

```{r,eval=FALSE}
global_df <- rbind(aero_epi_df,comb_epi_df,drop_epi_df)

remove(comb_epi_df,aero_epi_df,drop_epi_df) # delete useless variables
remove(r0_comb_df,r0_aero_df,r0_drop_df) # delete useless variables
```

# Plotting Distributions 
(fig. 3 of paper)

## plot epi. quant. distributions  for all 3 models
```{r}
itot_dist <- ggplot() + theme_bw() +
  geom_freqpoly(aes(x = global_df$mean_i_tot,
                   color = global_df$model)) +
  xlab('mean outbreak size') +
  theme(legend.position = 'none')

ttp_dist <- ggplot() + theme_bw() +
  geom_freqpoly(aes(x = global_df$mean_time_to_peak,
                   color = global_df$model)) +
  xlab('mean time-to-peak') +
  theme(legend.position = 'none')
    # scale_colour_discrete(name = 'Model type')

mt_dist <- ggplot() + theme_bw() +
  geom_freqpoly(aes(x = global_df$mean_max_time,
                   color = global_df$model)) +
  xlab('mean max time') +
  theme(legend.position = 'none')
  
```

## custom function to extract the legend from previous plot
```{r}

get_legend<-function(myggplot){
    tmp <- ggplot_gtable(ggplot_build(myggplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)
}

dist_leg <- get_legend(ttp_dist)

```

## plot  $R_{0}$ distribution for all 3 models
(remind that we use results from ACR05)

```{r}
r0_three_models_plot <- ggplot() + 
  theme_bw() +
  geom_boxplot(aes(x = global_df$model,y = global_df$mean_r0,
                   color = global_df$model)) +
  # scale_colour_discrete(name = 'Model type') +
  theme(legend.position = 'none') +
  
  ylab(expression('mean R\''[0] ) ) + 
  xlab('model type')

r0_three_models_plot

```


## merging  previous plots

```{r}
# (remember to first re-run the code for plotting with line 90 commented!)

# plot_grid(itot_dist,mt_dist,ttp_dist,dist_leg,
plot_grid(itot_dist,mt_dist,ttp_dist,r0_three_models_plot,
          ncol = 2,labels = c('A','B','C','D'))

plot_name <- paste0('all_3_dist_new')
dev.copy(cairo_pdf, paste0( plot_name,'.pdf'))
dev.off()

```

