---
title: "<center> Main figures for paper </center>"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
---

Loading packages 

```{r}
library("gridExtra")
library("ggplot2")
library(scales) # for function alpha()
library("moments", lib.loc="~/Library/R/3.2/library")
library("operators", lib.loc="~/Library/R/3.2/library")
library("cowplot", lib.loc="~/Library/R/3.2/library")
```

# Loading simulations outputs 

## custom function to load epi. quant. 
(only for 'combined' and 'pure-aerosol' models)

```{r,eval=FALSE}

epi_loading_fun <- function(my_path) {
  
  cond_subdir <- sort(list.dirs(my_path) )
  cond_subdir <- cond_subdir[-1] # eliminate the main folder from the list
  
  # create empty data-frame
  epi_quantities_df <- data.frame()

    for(sub_dir in cond_subdir) {
      
      if (grepl('vacc',my_path)==1){
          # get vacc. coverage
          school_cond <- as.numeric(strsplit(sub_dir,'[/]')[[1]][7]) 
      }
      
      else{
          # get ventilation 
          school_cond <- strsplit(sub_dir,'[/]')[[1]][7]
      }
      
      
        # list simulations , by idx-case 
        files <- sort(list.files(path= sub_dir,pattern="*.csv",full.names=T))
      
        for(f_name in files) {
          
          new_df<- read.csv(f_name, header=FALSE)
          idx<- new_df[1,1]
          
          # compute mean 
          epi_quantities_df <- rbind(epi_quantities_df,
                               data.frame(idx, 
                                          mean(new_df[,4]),
                                          mean(new_df[,5]),
                                          mean(new_df[,6]),
                                          school_cond ))
        }
    }
  
  # give right names, according to ventilation/vaccination
  if (grepl('vacc',my_path)==1){
    
    colnames(epi_quantities_df) <- c('idxc','mean_i_tot','mean_time_to_peak',
                                   'mean_max_time','vacc_cov')
  }
  else{
    
    colnames(epi_quantities_df) <- c('idxc','mean_i_tot','mean_time_to_peak',
                                   'mean_max_time','school_cond')
  }
  
  epi_quantities_df
}
```

## call loading function

```{r,eval=FALSE}

aero_df <- epi_loading_fun("~/Documents/school_net_proj/aerolsol_model_outputs")
aero_vacc_df <- epi_loading_fun("~/Documents/school_net_proj/vacc_cov_out") 

comb_1000_df <- epi_loading_fun("~/Documents/school_net_proj/1000_comb")
comb_vacc_1000_df <- epi_loading_fun("~/Documents/school_net_proj/1000_comb+vacc")

```

# Plotting figures for paper

## single model boxplots 

### computing median for different vacc. cov. 
```{r}
my_inter_comb <- tapply(comb_vacc_1000_df$mean_i_tot,comb_vacc_1000_df$vacc_cov,median)
my_inter_aero <- tapply(aero_vacc_df$mean_i_tot,aero_vacc_df$vacc_cov,median)
```

### extract  labels for legend 
```{r,eval=FALSE}
my_labels_comb <- sort(unique(comb_vacc_1000_df$vacc_cov))
```

### selecting the desired ACR 
```{r,eval=FALSE}
comb_to_plot <- comb_1000_df[comb_1000_df$school_cond %in% c('ACR05','ACR15','ACR30'),]
aerosol_to_plot <- aero_df[aero_df$school_cond %in% c('ACR05','ACR15','ACR30'),]
```

### plot results for combined model
```{r}
vacc_vent_comb <- ggplot() +  theme_bw() + ylim(0,20) +
    geom_hline(aes( yintercept = my_inter_comb,
                    colour = factor(my_labels_comb) )) +

    # scale_colour_discrete(name = 'Vacc. cov.(%)') +
    # scale_colour_discrete(name = bquote(atop('Vaccin.','cov. (%)'))) +
    theme(legend.position = 'none') +
    theme(text = element_text(size = 8)) +
    
    # scale_colour_gradient(name = 'Vaccination cov.(%)',
    # low = 'black', high = 'red' ) +
    
    geom_boxplot(aes(factor(comb_to_plot$school_cond),
                     comb_to_plot$mean_i_tot),
                 outlier.size = 0.3) +
    
    # ylab("outbreak size median")
    ylab("") + xlab('air change rate')  +
    scale_x_discrete(labels = c('0.5','1.5','3')) + 
    
    ggtitle('all-rooms') +
    
    annotate("text",label = "(combined)",
             x = 2, y = 20,size = 3)
             # , colour = "red")

# +
#     theme(axis.text.x = element_text(angle = 60, hjust = 1))
 
vacc_vent_comb

# plot_name <- paste0('vac_VS_combined')
# plot_name <- paste0('vac_VS_combined_1000')
# dev.copy(cairo_pdf, paste0( plot_name,'.pdf'))
# dev.off()

```

### plot results for aerosol model
```{r}
vacc_vent_aero <- ggplot() +  theme_bw() + ylim(0,20) +
    geom_hline(aes( yintercept = my_inter_aero,
                    colour = factor(my_labels_comb) )) +

    # scale_colour_discrete(name = bquote(atop('Vaccin.','cov. (%)')),
    
    # scale_colour_discrete(name = 'Vaccination coverage (%)',
    #                       guide = guide_legend(nrow = 1)) +
    # theme(legend.position="bottom",
    #       # legend.direction="horizontal",
    #       legend.box = "horizontal") +

    theme(legend.position = 'none') +

    theme(text = element_text(size = 8)) +
    # scale_colour_gradient(name = 'Vaccination cov.(%)',
    # low = 'black', high = 'red' ) +
    
    geom_boxplot(aes(factor(aerosol_to_plot$school_cond),
                     aerosol_to_plot$mean_i_tot),
                 outlier.size = 0.3) +
    
    ylab("outbreak size median") + xlab('air change rate') +
    scale_x_discrete(labels = c('0.5','1.5','3')) + 
    
    ggtitle('all-rooms') +
    
    annotate("text",label = "(aerosol)",
             x = 2, y = 20,size = 3)

# +
#     theme(axis.text.x = element_text(angle = 60, hjust = 1))
 
vacc_vent_aero

# plot_name <- paste0('vac_VS_aerosol')
# dev.copy(cairo_pdf, paste0( plot_name,'.pdf'))
# dev.off()

```


## boxplot for all ventilation strategies

### preparing ventilation-strategy-names

```{r}
cond_norm <- c('ACR05','ACR15','ACR30')
cond_opt <- c('ACR05_opt05','ACR05_opt10','ACR05_opt15','ACR05_opt20','ACR05_opt25')
cond_sch <- c('ACR05_sch05','ACR05_sch10','ACR05_sch15','ACR05_sch20','ACR05_sch25')
cond_siz <- c('ACR05_siz05','ACR05_siz10','ACR05_siz15','ACR05_siz20','ACR05_siz25')

comb_1000_df$strategy[comb_1000_df$school_cond %in% cond_norm] <- 'all-rooms'
comb_1000_df$strategy[comb_1000_df$school_cond %in% cond_opt] <- 'optimal'
comb_1000_df$strategy[comb_1000_df$school_cond %in% cond_sch] <- 'schedule-based'    
comb_1000_df$strategy[comb_1000_df$school_cond %in% cond_siz] <- 'size-corrected'    
```

```{r}
# custom funcion for 2nd x labels!
# credits to: http://stackoverflow.com/questions/18165863/multirow-axis-labels-with-nested-grouping-variables
```

### function to subplot single ventilation strategy
```{r}

single_strat_fun <- function(my_strategy){
    
    good_data <- comb_1000_df[comb_1000_df$strategy==my_strategy,]
    
    single_strat_subplot <- ggplot() + theme_bw() + ylim(0,20) +
        # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
        theme(text = element_text(size = 8)) +
        
        # plot vaccination medians
        geom_hline(aes( yintercept = my_inter_comb,
                        colour = factor(my_labels_comb))) +
        
        # plot ventilation medians
        geom_boxplot(aes(x = good_data$school_cond,y = good_data$mean_i_tot),
                     outlier.size = 0.3)  +
        
        xlab('school volume (%)') +
        ylab('') +
        ggtitle(my_strategy) +
                
        annotate("text",label = '(combined)',
             x = 3, y = 20,size = 3) +
        
        theme(legend.position = 'none')  +
        
        scale_x_discrete(labels = substr(unique(good_data$school_cond),
                                     start = 10,stop = 11))

    return(single_strat_subplot)
}

```

### merging the  6 subplots 
```{r}

c = 0.2
leg_y = 0.1

ggdraw() +
    draw_plot(boxplot_leg, x = 0, y = -0.45) +
              # , width = 0.01, height = 0.4) +
    draw_plot(vacc_vent_aero, x = 0 , y = leg_y, 0.2, 0.6) +
    draw_plot(vacc_vent_comb, x = 0.2 , y = leg_y, 0.2, 0.6) +
    draw_plot(single_strat_fun('optimal'), x = 0.4 , y = leg_y, 0.2, 0.6) +
    draw_plot(single_strat_fun('schedule-based'), x = 0.6 , y = leg_y, 0.2, 0.6) +
    draw_plot(single_strat_fun('size-corrected'), x = 0.8 , y = leg_y, 0.2, 0.6) +
    draw_plot_label(c('A','B','C'), c(0 , 0.2 , 0.4 ),
                    c(0.6 + leg_y, 0.6 + leg_y, 0.6 + leg_y), size = 10)

plot_name <- paste0('all_boxplots_1000_new')
dev.copy(cairo_pdf, paste0( plot_name,'.pdf')) #,height = 5)
dev.off()


```


###  plot with all ventilation strategies
```{r}

many_box_plots <- ggplot() + theme_bw() + ylim(0,20) +
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
    theme(text = element_text(size = 8)) +
    
    geom_hline(aes( yintercept = my_inter_comb,
                    colour = factor(my_labels_comb)))+
    
    geom_boxplot(aes(x = comb_1000_df$strategy,
                     y = comb_1000_df$mean_i_tot,
                     group = comb_1000_df$school_cond),
                 outlier.size = 0.3) + 
    
    # facet wrap makes impossible to add the hlines!
    # facet_wrap(~strategy,nrow = 1,scales = 'free_x') +
    
    ylab("outbreak size median")  + 
    xlab('school conditions - combined model')  +
    
    theme(legend.position = 'none') 
    # scale_colour_discrete(name = 'Vacc. cov.(%)')  +
    # scale_colour_discrete(name = bquote(atop('Vaccin.','cov. (%)'))) 

many_box_plots
```

### get legend from plot

```{r}
get_legend <- function(myggplot){
    tmp <- ggplot_gtable(ggplot_build(myggplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)
}

boxplot_leg <- get_legend(vacc_vent_aero)
```

## merging the  3 boxplots 
```{r}

ggdraw() +
    draw_plot(vacc_vent_comb, x = 0, y = 0, .2, 0.6) +
    draw_plot(vacc_vent_aero, x = 0.2, y = 0, .2, 0.6) +
    draw_plot(many_box_plots, x = 0.4, y = 0, .5, 0.6) +
draw_plot(boxplot_leg, x = 0.9, y = 0.25, .1, 0.2) +
    draw_plot_label(c('A','B','C'), c(0, 0.2, 0.4),
                    c(0.6, 0.6, 0.6), size = 10)

# plot_grid(vacc_vent_comb,vacc_vent_aero,many_box_plots,
#           # boxplot_leg,
#           labels = c('A','B','C',''),nrow = 1,
#           rel_widths = c(2,2,8)) 
#,scale = c(1,1,1,0.1))

plot_name <- paste0('all_boxplots_1000_new')
dev.copy(cairo_pdf, paste0( plot_name,'.pdf')) #,height = 5)
dev.off()

```


